\vspace{1.0cm} \LARGE \bf Revealing the competitive dynamics of influenza viruses through evolutionary cartography

### 2012-11-30 flux.tex
Include short (125-word) abstract.

>>>>

Influenza viruses undergo continual antigenic evolution allowing mutant viruses to evade immunity acquired by the host population to previous virus strains.
However, the extent to which antigenic evolution determines competitive dynamics within and between virus clades A/H3N2, A/H1N1, B/Victoria and B/Yamagata has remained unclear.
Here, we develope a novel cartographic approach to simultaneously characterize the genetic and antigenic evolution of viral lineages.
Through this approach, we determine historical rates and patterns of antigenic drift in all four viral clades and we show that antigenic drift influences year-to-year variability in clade dominance.
We investigate the selective underpinnings for differing antigenic dynamics across clades and suggest that pleiotropic effects linked to antigenic mutation determine selective outcomes.
